Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-06-15 automatica/paper.tex
Added SymEx section
SymEx section draft, detail level to be decided.

>>>>

\subsection{Symbolic execution}
We use the bounded model checker CBMC~\cite{ClarkeKL04} to model controller behaviour on digitial signals with finite
bit-precision.  We express these controller semantics as C programs, which is CBMC's preferred input language.  CBMC
symbolically executes every instruction in an input program by translating it to a boolean satisfiability problem.  At
the end of this process, the entire input program is translated to a boolean satisfiability formula which is satisfiable
iff a certain property about the program holds.  CBMC's API allows to specify these properties in the form of assertions
in the input program, and we use these properties to express that our generated controllers are modelled in a stable and
safe fashion. \note{Do we need more details here? Should we explain e.g. SSA or give examples of how assignments, loops,
etc. are turned into formulas? Part of Sec.~\ref{sec:errors} can probably be moved here.}
